---
title: "Corona Virus Report"
author:
- familyname: XXXX
  othernames: XXX
  address: Monash Universtidy
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)

```



\section*{Country XX1 and YY1"}

\section*{Country XX2 and YY2}

\section3{Country British Virgin Islands and Brunei Darussalam}

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(lubridate)
library(ggmap)
library(kableExtra)
```

```{r}
world_wide_cases <- read.csv("Data/worldwidecases.csv")
```

```{r}
british_brunei <- world_wide_cases %>% filter(countriesAndTerritories %in% c("British_Virgin_Islands", "Brunei_Darussalam"))
```

The countries I have chosen to work on are the British Virgin Islands and Brunei Darussalam.

```{r}
british_monthly_cases <- british_brunei %>% filter(countriesAndTerritories == "British_Virgin_Islands") %>%
mutate(Month = month(dateRep)) %>% select(Month, cases, deaths) %>% group_by(Month) %>% summarise(Total = sum(cases))
```

```{r british-monthly}
ggplot(british_monthly_cases) +
  geom_col(aes(x = Month, y = Total)) +
  theme_classic() +
  ggtitle("Total monthly cases for British Virgin Islands")
```

From (Figure \@ref(fig:british-monthly)), we can see that the total number of cases has been very low across the months of March, April and May. May reported the lowest number of total cases at 1.

```{r brunei-monthly}
(brunei_cases <- british_brunei %>% filter(countriesAndTerritories == "Brunei_Darussalam") %>%
mutate(Month = month(dateRep), Day = day(dateRep)) %>% select(Day, Month, cases, deaths) %>% group_by(Month) %>% summarise(Total = sum(cases)) %>% kable(caption = "Monthly Brunei Cases") %>% kable_styling(bootstrap_options = c("basic", "hovered")))
```

In (Table \@ref(tab:brunei_monthly)), the number of cases has been sharply declining from 127 cases to 11 to 3 cases in the months of March, April and May respectively.

